Select-based random access to variable-byte encodings

### 2020-03-01 gradu/msc_english_contents.tex
Changes

\draw[arrow] (Btarget.south) to (Atarget.north);
\end{tikzpicture}
\caption{Data} \label{VBarrays}
\end{figure}
TODO: try bitvector SD performance + size (select) (maybe write about different select implementations)

@@

All implementation read the data set from a file and compres it to memory. Then one million index integers are randomized to an array. The times shown in Table~\ref{table:results1} 
are times taken from looping through the index array and VB decoding the number in the index. Additionally, each run is iterated ten times and a mean of the run is taken.

>>>>

\draw[arrow] (Btarget.south) to (Atarget.north);
\end{tikzpicture}
\caption{Data} \label{VBarrays}
\end{figure}

@@

All implementations read the data set from a file and compress it to memory. Then one million index integers are randomized and stored to an array. The times shown in Table~\ref{table:results1} 
are times taken from looping through the index array and VB decoding the number in the index. Additionally, each run is iterated ten times and a mean of the run is taken.
